---
title: "Introduction to Programming in R"
author: "Mohammed Shahid"
date: "5/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# 1. Programming in R

```{r}
125-3
```
# 2. Literal values: Logicals

Use the logical literals (TRUE or FALSE) to indicate if these statements are correct or incorrect (write your answers in the order of the statements, one answer per line).

1. True represents the "true" literal in R.

```{r}
F
```

2. F or FALSE represents the "false" literal in R.

```{r}
T
```

3. No matter how we write "true" and "false" – TRUE, True, tRue, false – R interprets them as logical literals.

```{r}
F
```
# 3. Literal values: Numerics

Answer the following questions in order, one answer per line.

1. (Expected answer: TRUE or FALSE) In R, the literal value 1 is the Logical data type.

```{r}
FALSE
```


2. (Expected answer: corresponding literal value) By default, how will R represent this number 0.012?

```{r}
0.012
```



# 4. Literal values: Integers

Answer the following questions in order, one answer per line.

1. (Expected answer: TRUE or FALSE) To represent an integer literal, I (which means integer) precedes the numberic value.

```{r}
F
```

2. (Expected answer: corresponding literal value) Type 125 appropriately to ensure that R considers it as an integer literal.

```{r}
125L
```
# 5. Literal values: Character

Use the character literals "Agree" or "Disagree" to answer the following questions.

1. The literal value T is a literal value of Character data type.

```{r}
"Disagree"
```


2. To represent a character literal, you must always precede it with a quotation mark and follow it with an apostrophe (e.g., "Good Morning').

```{r}
"Disagree"
```


3. A letter (e.g., "A") is not a Character data type.

```{r}
"Disagree"
```


4. R interprets a number as a number only if we do not enclose it in quotation marks or apostrophes.

```{r}
"Agree"
```
# 6. Arithmetic operators: simple expression

|   | day | supply Day | item      | purchase Price | selling Price | item available | item sold |
|---|-----|------------|-----------|----------------|---------------|----------------|-----------|
| 1 | 1L  | TRUE       | "Apple"   | 10.50          | 12.10         | 200L           | 0L        |
| 2 | 1L  | TRUE       | "Mangoes" | 21.15          | 24.90         | 50L            | 0L        |
| 3 | 1L  | TRUE       | "Lemon"   | 3.20           | 4.99          | 500L           | 0L        |
| 4 | 2L  | FALSE      | "Apple"   | 10.50          | 12.10         | 188L           | 12L       |
| 5 | 2L  | FALSE      | "Mangoes" | 21.15          | 24.90         | 47L            | 3L        |
| 6 | 2L  | FALSE      | "Lemon"   | 3.20           | 4.99          | 476L           | 24L       |

Write the operations that answer the following questions.

1. The profit (selling price minus purchase price) on the sale of a mango using values in the purchase price and selling price columns.

```{r}
24.9-21.15
```


2. The overall mangoes revenue (selling price multiplied by the number of units sold) on day 2 using values in the item sold and selling price columns.

```{r}
24.9*3L
```
3. (Answer this question with TRUE or FALSE literals) The multiplication operator, in R, is the same as it is in mathematics: x (e.g., 3 x 4).

```{r}
FALSE
```


# 7. R syntax

Write this program in the Code Editor.

```{r}
#FALSE
#TRUE FALSE
```

To correct the error, we need to split the second line in two as follows.

```{r}
FALSE
TRUE
FALSE
```
# 8. Next Steps

Congratulations! You have completed the first lesson in the Introduction to Programming in R course.

In this lesson, you learned some key basics of programming in R:

* Working with literals
* Writing simple expressions
* Following R syntax

On the next screen, you'll find a summary of what you've learned so far: a handy list of takeaways you can refer back to as you continue learning R for data science.

In the next lesson, we'll continue learning R syntax. We'll discover the concept of variable and the complex arithmetic expressions and their rules.

For now, click the Next button below to read and download the summary of this lesson. On the next screen, you'll also be able to click the Finish button, which will mark this lesson as complete for you.


