---
title: "Arithmetic Expressions and Variables in R"
author: "Mohammed Shahid"
date: "5/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Revisiting Common arithmetic operators


|   | day | supply Day | item      | purchase Price | selling Price | item available | item sold |
|---|-----|------------|-----------|----------------|---------------|----------------|-----------|
| 1 | 1L  | TRUE       | "Apple"   | 10.50          | 12.10         | 200L           | 0L        |
| 2 | 1L  | TRUE       | "Mangoes" | 21.15          | 24.90         | 50L            | 0L        |
| 3 | 1L  | TRUE       | "Lemon"   | 3.20           | 4.99          | 500L           | 0L        |
| 4 | 2L  | FALSE      | "Apple"   | 10.50          | 12.10         | 188L           | 12L       |
| 5 | 2L  | FALSE      | "Mangoes" | 21.15          | 24.90         | 47L            | 3L        |
| 6 | 2L  | FALSE      | "Lemon"   | 3.20           | 4.99          | 476L           | 24L       |


Write the operations that answer the following questions.

1. The total number of mangoes and lemons available in the shop on day 2 using values in the item available column.

* Sum up the number of mangoes (47L) and lemons (476L) on day 2 using the addition operator +.

```{r}
47+476
```


2.The ratio of the purchase price of lemon against its selling price using values in purchase price and selling price columns.

* Divide the purchase price of lemon (3.20) by its selling price (4.99) using the division operator /.

```{r}
3.20/4.99
```

# 2. Dealing with Advanced Arithmetic Operators


|   | day | supply Day | item      | purchase Price | selling Price | item available | item sold |
|---|-----|------------|-----------|----------------|---------------|----------------|-----------|
| 1 | 1L  | TRUE       | "Apple"   | 10.50          | 12.10         | 200L           | 0L        |
| 2 | 1L  | TRUE       | "Mangoes" | 21.15          | 24.90         | 50L            | 0L        |
| 3 | 1L  | TRUE       | "Lemon"   | 3.20           | 4.99          | 500L           | 0L        |
| 4 | 2L  | FALSE      | "Apple"   | 10.50          | 12.10         | 188L           | 12L       |
| 5 | 2L  | FALSE      | "Mangoes" | 21.15          | 24.90         | 47L            | 3L        |
| 6 | 2L  | FALSE      | "Lemon"   | 3.20           | 4.99          | 476L           | 24L       |


Write the operations that answer the following questions.

1. Assuming the selling price of lemon is \$5, how many lemons were sold if $128 is reported as the overall selling cost of a day. Use the integer division operator, %/%, to answer this question.

```{r}
128 %/% 5
```


2. (Answer this question with TRUE or FALSE literals instead) The modulo's operator symbol is %.


```{r}
FALSE
```

# 3. Using Complex Arithmetic Expression


1. Your mission is to determine the overall cost of purchasing all fruits on day 1.

Type in the code editor the following operations.

* The total cost of purchasing apples on day 1: 10.50 * 200L.

```{r}
10.50 * 200L
```

* The total cost of purchasing mangoes on day 1: 21.15 * 50.
```{r}
21.15*50
```


* The total cost of purchasing lemons on day 1: 3.20 * 500.

```{r}

3.20*500
```
2. Compute the overall cost of purchasing all fruits on day 1, in a single expression.

* Sum up the output values from the previous question.

```{r}
10.50 * 200L + 21.15*50 + 3.20*500
```

# 4. Dealing with Operator Priority Rules

1. Your mission is to determine the overall predicted selling cost of all fruits on day 1.

Type in the code editor the following operations.

* The predicted selling cost of apples on day 1: 12.10 * 200L.

```{r}
12.10 * 200L
```


* The predicted selling cost of mangoes on day 1: 24.90 * 50L.

```{r}
24.90 * 50L
```
* The predicted selling cost of lemons on day 1: 4.99 * 500L.

```{r}
4.99 * 500L
```
2. Compute the overall predicted selling cost of all fruits on day 1.

* Combine the previous three simple expressions into a complex expression using the addition operator.

```{r}
12.10 * 200L+24.90 * 50L+4.99 * 500L
```

# 5. Identifying Expression's data type

Use one of this character literals ("numeric" or "integer" or "logical") to answer the following questions.

1. What is the type of the following expression: 2 * 2 * 2.

```{r}
"numeric"
```


2. What is the type of the following expression: 2L * 2L * 2.

```{r}
"numeric"
```


3. What is the type of the following expression: 2L * 2L * 2L.

```{r}
"integer"
```
# 6. Dealing Variables with Naming rules

To name a variable, there are five naming rules to follow.

1. Variable names consists of letters (upper or lower case), numbers, a dot (.), or an underscore (_).
2. We can begin a variable name with a letter or a dot, but dots cannot be followed by a number.
3. We cannot begin a variable name with a number.
4. No special characters are allowed, e.g., spaces, operator's symbols, ", parentheses.
5. We cannot use a keyword already used and interpreted by R as a variable name.

Here is a list of variable names, numbered from 1 to 5. Using naming rules, answer TRUE if the variable name is valid and FALSE otherwise. Store each answer (TRUE/FALSE) in variables named q_1 to q_5, respectively (one answer per line). An example is given in the editor.

1. .2var
2. numberOfFruit
3. apple variable
4. "var"
5. age20+

```{r}
q_0 <- FALSE
q_1=F
q_2=T
q_3=F
q_4=F
q_5=F
```

# 7. Updating variables

```{r}
total_purchase_cost=10.50 * 200L + 21.15 * 50L + 3.20 * 500L

total_selling_cost=12.10 * 200 + 24.90 * 50 + 4.99 * 500

profit_1=total_selling_cost-total_purchase_cost

print(profit_1)
```

# 8. Identifying variables data type

